Brownian Dynein Model

### 2015-08-22 latex/derivation.tex
Update dynein_struct.cpp with new angular velocity matrix terms.

\begin{align}
  C_1 &= -3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\\
  C_2 &= -3L_{t}\\
  C_3 &= +2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\\
  C_4 &= + L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\\
  X_3 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))\\
      &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
\end{align}

>>>>

\begin{align}
  B_1 &= -3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\\
  B_2 &= -3L_{t}\\
  B_3 &= +2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\\
  B_4 &= + L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\\
  X_2 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))\\
      &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
\end{align}
